### 2009-03-22 doc/storage_system/arc-storage-documentation.tex
documentation about the STALLED state

A file in the ARC storage has a logical entry in the namespace, and a couple of physical replicas on the storage nodes. We store the locations of the replicas in the \emph{location} section. A location contains the URL of the Shepherd service, the local ID of the file within the storage node and the state of the replica. This state could be `\textbf{alive}' (if the replica passed the checksum test, and the Shepherd reports that the storage node is healthy), `\textbf{invalid}' (if the replica has wrong checksum, or the Shepherd claims it has no such file), `\textbf{offline}' (if the Shepherd is not reachable, but may have a valid replica), `\textbf{creating}' (if the replica is in the state of uploading), `\textbf{thirdwheel}' (if the replica is marked for deletion because of too many replicas). We also store (in the \emph{states} section) the size of the file, the number of needed replicas, and a checksum of the file, which is created by some kind of checksumming algorithm (currently only md5 is supported).

@@

    The \emph{filelist} is a list of (\emph{GUID}, \emph{referenceID}, \emph{state}) tuples containing the state of changed or new files, where referenceID is the Sheperd-local ID of the given replica where GUID refers to the logical file of this replica. The \emph{state} could be `\textbf{invalid}' (if the periodic self-check of the Shepherd found a non-matching checksum or missing file), `\textbf{creating}' (if this is a new file not uploaded yet) or `\textbf{alive}' (if the file is uploaded and the checksum is OK).

@@

The replicas have a state, which could be `\textbf{creating}' when the transfer is initiated but the file is not uploaded yet, `\textbf{alive}' if the file is uploaded and has a proper checksum, or `\textbf{invalid}' if it does not exists anymore or has a bad checksum.

@@

\begin{description}
    \item[ServiceID] is the ID of the service, currently it should be the URL of the service, because there is no information system where we can discover services by IDs.
    \item[CheckPeriod] specifies in seconds how frequently should the Shepherd check the existence and the checksum of all the files on the storage node.
    \item[MinCheckInterval] specifies in seconds how much time should the Shepherd wait between two subsequent file checks. This ensures that the Shepherd does not use up all the resources of the hosting machine. After checking the cheksum of a file, the Shepherd will always wait this long before checking the next file, even if this means that checking all the files takes longer than the `CheckPeriod'.
    \item[StoreClass] specifies which type of store the Shepherd should use for storing its metadata on disk.
    \item[StoreCfg] can have parameters for the store class, e.g. the local directory to be used.
    \item[BackendClass] specifes which backend the Shepherd should use for communicating with the storage element service.
    \item[BackendCfg] has some configuration parameters for the backend class: \textbf{DataDir} and \textbf{TransferDir} is the directories the backend will use (see Section~\ref{sub:shepherd_implementation}), \textbf{TURLPrefix} should be the URL of the storage element service ending with a `/'.
    \item[LibrarianURL] is the URL of a Librarian where the Shepherd should send the reports.
    \item[BartenderULR] is the URL of a Bartender whom the Shepherd should connect if it wants to offer a replica for replication or recover a corrupted replica.
\end{description}

\begin{verbatim}
    <Service name="pythonservice" id="shepherd">
        <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
        <ServiceID>https://localhost:60000/Shepherd</ServiceID>
        <CheckPeriod>20</CheckPeriod>
        <MinCheckInterval>0.1</MinCheckInterval>
        <StoreClass>storage.store.cachedpicklestore.CachedPickleStore</StoreClass>
        <StoreCfg>
            <DataDir>./shepherd_data1</DataDir>
        </StoreCfg>
        <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
        <BackendCfg>
            <DataDir>./shepherd_store</DataDir>
            <TransferDir>./shepherd_transfer</TransferDir>
            <TURLPrefix>https://localhost:60000/hopi/</TURLPrefix>
        </BackendCfg>
        <LibrarianURL>https://localhost:60000/Librarian</LibrarianURL>
        <BartenderURL>https://localhost:60000/Bartender</BartenderURL>
        <ClientSSLConfig FromFile="clientsslconfig.xml"/>
    </Service>    
\end{verbatim}

>>>>

A file in the ARC storage has a logical entry in the namespace, and a couple of physical replicas on the storage nodes. We store the locations of the replicas in the \emph{location} section. A location contains the URL of the Shepherd service, the local ID of the file within the storage node and the state of the replica. This state could be `\textbf{alive}' (if the replica passed the checksum test, and the Shepherd reports that the storage node is healthy), `\textbf{invalid}' (if the replica has wrong checksum, or the Shepherd claims it has no such file), `\textbf{offline}' (if the Shepherd is not reachable, but may have a valid replica), `\textbf{creating}' (if the replica is in the state of uploading), `\textbf{thirdwheel}' (if the replica is marked for deletion because of too many replicas), `\textbf{stalled}' (if the the replica was in the state if uploading for a long time but hasn't arrived). We also store (in the \emph{states} section) the size of the file, the number of needed replicas, and a checksum of the file, which is created by some kind of checksumming algorithm (currently only md5 is supported).

@@

    The \emph{filelist} is a list of (\emph{GUID}, \emph{referenceID}, \emph{state}) tuples containing the state of changed or new files, where referenceID is the Sheperd-local ID of the given replica where GUID refers to the logical file of this replica. The \emph{state} could be `\textbf{invalid}' (if the periodic self-check of the Shepherd found a non-matching checksum or missing file), `\textbf{creating}' (if this is a new file not uploaded yet), `\textbf{thirdwheel}' (if the replica is marked for deletion because of too many replicas), `\textbf{alive}' (if the file is uploaded and the checksum is OK), or `\textbf{stalled}' (if the file was in `creating' state for a long time but hasn't arrived).

@@

The replicas have a state, which could be `\textbf{creating}' when the transfer is initiated but the file is not uploaded yet, `\textbf{alive}' if the file is uploaded and has a proper checksum, `\textbf{invalid}' if it does not exists anymore or has a bad checksum, `\textbf{thirdwheel}' if the replica is marked for deletion because the file has too many replicas, or `\textbf{stalled}' if it was in a `creating' state for a long time but hasn't arrived.

@@

\begin{description}
    \item[ServiceID] is the ID of the service, currently it should be the URL of the service, because there is no information system where we can discover services by IDs.
    \item[CheckPeriod] specifies in seconds how frequently should the Shepherd check the existence and the checksum of all the files on the storage node.
    \item[MinCheckInterval] specifies in seconds how much time should the Shepherd wait between two subsequent file checks. This ensures that the Shepherd does not use up all the resources of the hosting machine. After checking the cheksum of a file, the Shepherd will always wait this long before checking the next file, even if this means that checking all the files takes longer than the `CheckPeriod'.
    \item[CreatingTimeout] specifies in seconds after how much time the Shepherd decideds that a started file upload won't happen. This is not fatal, if the file is uploaded eventually, it will be a valid replica, but after this much time the system starts creating new replicas just in case.
    \item[StoreClass] specifies which type of store the Shepherd should use for storing its metadata on disk.
    \item[StoreCfg] can have parameters for the store class, e.g. the local directory to be used.
    \item[BackendClass] specifes which backend the Shepherd should use for communicating with the storage element service.
    \item[BackendCfg] has some configuration parameters for the backend class: \textbf{DataDir} and \textbf{TransferDir} is the directories the backend will use (see Section~\ref{sub:shepherd_implementation}), \textbf{TURLPrefix} should be the URL of the storage element service ending with a `/'.
    \item[LibrarianURL] is the URL of a Librarian where the Shepherd should send the reports.
    \item[BartenderULR] is the URL of a Bartender whom the Shepherd should connect if it wants to offer a replica for replication or recover a corrupted replica.
\end{description}

\begin{verbatim}
    <Service name="pythonservice" id="shepherd">
        <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
        <ServiceID>https://localhost:60000/Shepherd</ServiceID>
        <CheckPeriod>20</CheckPeriod>
        <MinCheckInterval>0.1</MinCheckInterval>
        <CreatingTimeout>600</CreatingTimeout>
        <StoreClass>storage.store.cachedpicklestore.CachedPickleStore</StoreClass>
        <StoreCfg>
            <DataDir>./shepherd_data1</DataDir>
        </StoreCfg>
        <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
        <BackendCfg>
            <DataDir>./shepherd_store</DataDir>
            <TransferDir>./shepherd_transfer</TransferDir>
            <TURLPrefix>https://localhost:60000/hopi/</TURLPrefix>
        </BackendCfg>
        <LibrarianURL>https://localhost:60000/Librarian</LibrarianURL>
        <BartenderURL>https://localhost:60000/Bartender</BartenderURL>
        <ClientSSLConfig FromFile="clientsslconfig.xml"/>
    </Service>    
\end{verbatim}
